\documentclass[11pt]{article}

\usepackage{latexsym}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{nopageno}
\usepackage{changepage}
\usepackage{fontawesome}
\usepackage[a4paper, top=0.2in, left=0.3in, right=0.3in, bottom=0.2in]{geometry}

% Setup appearance of hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=RoyalBlue,
    urlcolor=RoyalBlue,
}
\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Changing bullet styles
\renewcommand{\labelitemi}{$$}
\renewcommand{\labelitemii}{$\circ$}

%-------------------------
% Custom commands
\newcommand{\resumeSubItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-4pt}}
  }
}

% All commands required to define list of job descriptions
\newcommand{\jobDescriptionsListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\jobDescription}[5]{  % Args order [5]: Company name, location, position, time, project description
  \vspace{-1pt}
  \item
    \begin{tabular*}{0.99\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small #3} & \textit{\small #4} \\
    \end{tabular*}
    \\*[3pt]

    \begin{adjustwidth}{10pt}{}
    #5\vspace{-8pt}
    \end{adjustwidth}
}
\newcommand{\jobDescriptionsListEnd}{\end{itemize}}

% All commands required to define list of achievements for specific job
\newcommand{\jobAchievementsListStart}{\begin{itemize}}
\newcommand{\jobAchievement}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}
\newcommand{\jobAchievementsListEnd}{\end{itemize}\vspace{-4pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\huge Vladyslav Sydorenko} & \href{mailto:vladyslav.sydorenko@gmail.com}{vladyslav.sydorenko@gmail.com}\\
  \href{https://www.linkedin.com/in/vlad-sydorenko/}{linkedin.com/in/vlad-sydorenko/} & +1 (206) 503-32-37\\
  & \faMapMarker\ Seattle, WA, 98122
\end{tabular*}


%-----------EXPERIENCE-----------------
\vspace{-15pt}
\section{Experience}
  \jobDescriptionsListStart
    \jobDescription
      {Amazon Web Services}{Seattle, WA}
      {Software Development Engineer}{October 2018 - Current}
      {Member of a team responsible for control plane of storage layer for Amazon Aurora - fully managed cloud-native relational database.}
      \jobAchievementsListStart
        \jobAchievement{Implemented framework to validate stability of different services after OS patching.}
        \jobAchievement{Worked on framework for automated testing of project dependency outages handling (e.g. metadata storage outage).}
        \jobAchievement{Helped to reduce operational costs by automating cleanup of unused and leaked resources.}
        \jobAchievement{Refactored billing logic in order to optimise metadata storage utilization.}
      \jobAchievementsListEnd

    \jobDescription
      {RetailMeNot Inc. [via SoftServe]}{Kyiv, Ukraine}
      {Senior Software Engineer / Team Lead}{March 2017 - September 2018}
      {I led a team of developers responsible for highly-loaded and distributed service that performed automated checks of digital coupons validity and gift cards balances for more than 200 merchants in different countries.}
      \jobAchievementsListStart
        \jobAchievement{Worked as an engineering lead for distributed team of up to 9 developers.}
        \jobAchievement{Helped to improve percentage of successful validation tasks from 87\% to 96\%.}
        \jobAchievement{Participated in development of new subservice for automated testing of \href{https://www.retailmenot.com/genie/}{RMN Genie} - browser extension that applies digital coupons for you.}
        \jobAchievement{Set up full CI/CD system with Jenkins/Ansible/Packer instead of manual deployment process.}
        \jobAchievement{Migrated multiple system components from Python 2 to Python 3.}
      \jobAchievementsListEnd

    \jobDescription
      {Cisco [via SoftServe]}{Kyiv, Ukraine}
      {Software Engineer}{August 2016 - March 2017}
      {Worked on refactoring and bugfixing of Cisco Content Security Management Appliance (\href{https://www.cisco.com/c/en/us/products/security/content-security-management-appliance/index.html}{SMA}) software. Cisco SMA is a hardware appliance, that allows you to manage clusters of other hardware security appliances by Cisco, as well as centralize configuration management and reporting.}
      \jobAchievementsListStart
        \jobAchievement{Had experience working with codebase that contained more than 5 millions lines of code.}
        \jobAchievement{Successfully delivered project on time.}
      \jobAchievementsListEnd

    \jobDescription
      {Avtobazar}{Kyiv, Ukraine}
      {Junior Software Engineer}{June 2015 - August 2016}
      {Was working as a full-stack developer for \href{https:\\ab.ua}{ab.ua} - one of the biggest Ukrainian car selling marketplaces.}
      \jobAchievementsListStart
        \jobAchievement{Reachitectured processing of media files, including storage, caching and UI interface for management.}
        \jobAchievement{Worked on splitting monolithic application into multiple RESTful services.}
      \jobAchievementsListEnd

  \jobDescriptionsListEnd

%-----------EDUCATION-----------------
\section{Education}
  \jobDescription
      {National Technical University of Ukraine "Igor Sikorsky Kyiv Politechnic Institute"}
      {}
      {Bachelor of Science in Computer Engineering; GPA: 3.5}
      {}

\renewcommand{\labelitemi}{$\circ$}
%-----------Extracurricular Activities-----------------
\section{Extracurricular Activities}
    \subsection*{Hackathons}
      \begin{itemize}
        \resumeSubItem{CactusHack Kyiv 2016 - 1st place}
          {In 48 hours with a team of 2 developers implemented ML-based platform for remote learning, that had features like attention tracking, live streaming and fraud protection.}
        \resumeSubItem{AngelHack Lviv 2016 - Finalist}{Developed prototype of GitHub-like system for musicians to collaborate on projects, with features like preservation of history of changes, visualization of notes sheet and online editor.}
        \vspace{-7pt}
      \end{itemize}
    \subsection*{Certifications}
        \begin{itemize}
            \resumeSubItem{Leadership Development Program alumnus}{Graduated 9 months long internal program at SoftServe, created for potential managers and project leaders.}
            \resumeSubItem{Brainbench Python 3.4 certification}{Scored 4.53/5.0. At the time of passing was in top 20 in the world. \href{https://www.brainbench.com/transcript.jsp?pid=13466801}{Link to the transcript.}}
        \vspace{-7pt}
        \end{itemize}
    \subsection*{Other}
        \begin{itemize}
            \resumeSubItem{Talk: "Internals of CPython memory"}
              {Delivered a talk at KyivPy 2017 meetup: \href{https://youtu.be/-99tauPppoI?t=1}{link to the talk} }
            \resumeSubItem{Interests}{Highload and distributed systems.}
        \end{itemize}

%-------------------------------------------
\end{document}
